D3064R0: How to Avoid OOTA Without Really Trying

### 2024-03-05 ootavacuous.tex
"Non-LB Litmus Test": Reword
Signed-off-by: Paul E. McKenney <paulmck@kernel.org>

Most of the examples in this paper involve simple semantic dependencies
connecting a single load to a single store.
One exception appears in
Appendix~\ref{app:Non-LB Litmus Tests},
but this section will present a more difficult example.

@@

\subsection{Non-LB Litmus Tests}
\label{app:Non-LB Litmus Tests}

@@

Note that in a C++ implementation that (erroneously) permitted an OOTA
cycle to form, that cycle would involve both \co{r0} and \co{r1}.

>>>>

Most of the examples in this paper involve simple semantic dependencies
connecting a single load to a single store.
One exception appears in
Appendix~\ref{app:Non-LB Litmus Test},
but this section will present a more difficult example.

@@

\subsection{Non-LB Litmus Test}
\label{app:Non-LB Litmus Test}

@@

Note that in a C++ implementation that (erroneously) permitted an OOTA
cycle to form, that cycle would involve both of \co{P0()}'s \co{r0}
and \co{r1} local variables.
